How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-11 outputs/paper/paper.qmd
simulated data and tests

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
library(tidyverse)
library(sf)
library(readxl)
library(knitr)
library(janitor)
library(lubridate)
library(dplyr)
library(data.table)
library(RColorBrewer)
library(ggpubr)
library(scales)

@@

ghs_data <- read_excel(here::here("inputs/data/GHS_index.xlsx"))
world_map <- st_read(here::here("inputs/data/world/World_Countries__Generalized_.shp"))
life_exp <- read.csv(here::here("inputs/data/life_table.csv"), stringsAsFactors = FALSE)
vote_share <- read.csv(here::here("inputs/data/Vote_share_2020_data.csv"), stringsAsFactors = FALSE)
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
library(tidyverse)
library(sf)
library(readxl)
library(knitr)
library(janitor)
library(lubridate)
library(dplyr)
library(data.table)
library(RColorBrewer)
library(ggpubr)
library(scales)
library(here)

@@

#ghs_data <- read_excel(here::here("inputs/data/GHS_index.xlsx"))
#world_map <- st_read(here::here("inputs/data/world/World_Countries__Generalized_.shp"))
#life_exp <- read.csv(here::here("inputs/data/life_table.csv"), stringsAsFactors = FALSE)
#vote_share <- read.csv(here::here("inputs/data/Vote_share_2020_data.csv"), stringsAsFactors = FALSE)
ghs_data <- read_excel("C:/Users/35911/Documents/US-Covid-Analysis/inputs/data/GHS_index.xlsx")
world_map <- st_read("C:/Users/35911/Documents/US-Covid-Analysis/inputs/data/world/World_Countries__Generalized_.shp")
life_exp <- read.csv("C:/Users/35911/Documents/US-Covid-Analysis/inputs/data/life_table.csv", stringsAsFactors = FALSE)
vote_share <- read.csv("C:/Users/35911/Documents/US-Covid-Analysis/inputs/data/Vote_share_2020_data.csv", stringsAsFactors = FALSE)
